Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-21 src-latex/parts/30-dataset.tex
Add small precision about valid entries in XP2

These are the pieces of information that we want to extract, deduplicate  and structure to build a spatio-temporal database.
Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory/index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

\subsection{A dataset for OCR and NER evaluation}

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H} do not even have a Unicode codepoint, and were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalization was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

>>>>

These are the pieces of information we want to extract, deduplicate and structure to build a spatio-temporal database.
Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory/index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

\subsection{A dataset for OCR and NER evaluation}
\label{sec:dataset-for-eval}

@@

%1. Entrée/Sortie de l'OCR
\textbf{OCR stage.} The first stage of the pipeline aims at extracting the raw text from the images. An OCR system runs
on the thumbnails of each segmented entry to extract its text. An entry might span over multiple text lines but is
always a single block. Thus, the most adapted mode is chosen when the OCR system allows for the detection mode (e.g. the
\emph{block} mode for \emph{Tesseract}). 
Some glyphs used in this dataset might be unknown to the OCR, and some like
\scalerel*{\includegraphics{./images/LH.png}}{H} do not even have a Unicode codepoint, and were annotated using Unicode Private User Area 1.
Furthermore, as some annotations guidelines where unclear to human annotators, some projections rules were applied: whitespace, dash, dots and a couple of commonly confused characters where projected to well-defined codepoints.
The same normalisation was applied to OCR predictions.
At the end of this first stage, an OCR Quality Assessment (Q.A.) between the \emph{normalised} groundtruth text and the
OCR output is performed on the basis of the $8,765$ entries which were manually controlled, totalling $424,764$ characters (including $54,387$ spacing characters). Entries are $49.0$-characters long on average.

### 2022-01-21 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the French corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pretrained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using \num{845000} entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

%First, we split the ground truth into a training set, a development set, and a test set. 
%The training set is then gradually reduced in size while maintaining the relative frequency of directories within it.
As the structure of entries varies across directories, the models may learn to overfit on a subset of directories with specific features. 
To reduce the evaluation bias, we start by leaving out 3 directories (1690 entries, $\approx 19\%$) from the ground truth as a test set containing entries from unseen directories.

Then, a stratified sampling based on the source directory of each entry is run on the remainder to create a training set (6373 entries, $\approx 73\%$ of the gold reference) and a development set (709 entries, $\approx 8\%$).
The development set is used to evaluate the model during the training phase.
This resampling procedure is a convenient way to shape both sets, so they reflect the diversity of directories within the ground truth.

@@

The three models are fine-tuned on the NER task 5 times using each of the 8 training subsets, with an early stopping criterion based on the number of training steps without improvement of the F1-score. 
This patience threshold is set to 1600 steps for SpaCy NER and 3 evaluations (1 evaluation every 100 steps) for CmBERT and CmBERT+ptrn.
The metrics are measured for the 24 resulting NER models on the common test set and averaged over the runs.

>>>>

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the French corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pre-trained on Paris directories~[CmBERT+ptrn]}: 
To evaluate whether adapting CamemBERT to the domain increases its performance, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using approx. $845,000$ entries randomly sampled and OCRed with PERO.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

@@

%First, we split the ground truth into a training set, a development set, and a test set. 
%The training set is then gradually reduced in size while maintaining the relative frequency of directories within it.
As the structure of entries varies across directories, the models may learn to overfit on a subset of directories with specific features. 
To reduce the evaluation bias, we start by leaving out 3 directories ($1,690$ entries, $\approx 19\%$) from the ground truth as a test set containing entries from unseen directories.

Then, a stratified sampling based on the source directory of each entry is run on the remainder to create a training set ($6,373$ entries, $\approx 73\%$ of the gold reference) and a development set (709 entries, $\approx 8\%$).
The development set is used to evaluate the model during the training phase.
This resampling procedure is a convenient way to shape both sets, so they reflect the diversity of directories within the ground truth.

@@

The three models are fine-tuned on the NER task 5 times using each of the 8 training subsets, with an early stopping criterion based on the number of training steps without improvement of the F1-score. 
This patience threshold is set to $1,600$ steps for SpaCy NER and 3 evaluations (1 evaluation every 100 steps) for CmBERT and CmBERT+ptrn.
The metrics are measured for the 24 resulting NER models on the common test set and averaged over the runs.

### 2022-01-21 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex

We leverage the labeled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain 8341 entries (see \cref{sec:dataset-for-eval}), the produced train sets (resp. development and test) contain 6004 entries - 72\% of the total (resp. 668 - 8\% and 1669 - 20\%).

>>>>

We leverage the labeled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain $8,341$ entries (see \cref{sec:dataset-for-eval}), the produced train sets (resp. development and test) hold $6,004$ entries - 72\% of the total (resp. 668 - 8\% and $1,669$ - 20\%).
